Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-03-01 main_paper.tex
Remove the disclaimer from the first page
I think the paper is far enough along now that we don't need to act
like we're ashamed of it. So I've removed the notice to not 'cite or
circulate' from the first page.
Start mathematical appendix on a new page
Revise the application part
Now only focus on the mortality and education for only one cohort.

\paragraph{Important message from the authors:} This version of the paper is
very preliminary and incomplete. We have sent out a few early copies to get
feedback, but there are still serious errors that we have not addressed. Please
do not cite this paper or circulate it in its current form.

\newpage
\section{Introduction}
Regression Discontinuity (RD) designs have emerged in the last decade as an
important and popular research design strategy for analyzing the causal impact
of policies and interventions in several fields of the social sciences,
including economics, political science, public policy, and sociology.
This research strategy exploits the fact that many programs use somewhat
arbitrary thresholds to determine whether or not to provide a ``treatment,''
usually relying on some type of score, which this literature calls a ``running
variable.'' In its basic version, the sharp RD,  individuals or groups with score above a
certain threshold receive treatment while the ones below that cutoff are left
untreated.
The identification of the treatment effect at the threshold is then based on
comparing treated and untreated units at the cutoff. When a subject's
position just above or below the cutoff is credibly not related to
other factors impacting outcomes, including their unobserved
characteristics, differences between treated and untreated individuals
at the cutoff can be plausibly attributed to the treatment alone. As a
practical matter this involves comparing units within a bandwidth just
above and just below the threshold.

@@

Since the conditions for identification only need to hold in a neighborhood
around the cutoff, $\mu_+$ and $\mu_-$ can be estimated by extrapolating from a
local polynomial regression.  We will focus here on local linear
regression.\footnote{%
  See \cite{HTV2001}, \cite{Porter03} or \cite{FanGijbels92} for discussions of
  the properties of local polynomial regressions for boundary problems. The
  bootstrap algorithm proposed in this paper can be extended to accommodate
  higher order polynomials discontinuities in the derivatives of the conditional
  expectation, like ``Kink RD'' design \citep{card2009b}.} %
For this model, if $h$ represents a bandwidth parameter, the estimator of
$\tau$, $\hat\tau(h)$, is defined as
\begin{equation*}
  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
\end{equation*}
with
\begin{align*}
  (\hat {\mu}_{+}(h),\ \hat {\mu}^{(1)}_{+}(h))'
  &= \argmin_{\mu, \beta} \sum_{i=1}^{n}
  \1\{h > X_{i} \geq 0\} (Y_{i} - \mu - X_{i} \beta)^{2}
\intertext{and}
  (\hat {\mu}_{-}(h),\hat {\mu}^{(1)}_{-}(h))'
  &= \argmin_{\mu,\beta} \sum_{i=1}^{n}
  \1\{0 > X_{i} > -h \} (Y_{i} - \mu - X_{i} \beta)^{2}.
\end{align*}
Conventional (naive) confidence intervals can be calculated by using an
asymptotic approximation for $\hat\tau(h)$. In particular, if
\begin{gather}
  \label{eq:1}
  \frac{\hat{\tau}(h)-\tau}{\sqrt{V(h)}} \to^d N(0,1),
  \intertext{with}
  \notag
  V(h) \big/ \V(\hat\tau(h) \mid X_{1},\dots,X_{n}) \to^p 1
\end{gather}
then valid confidence intervals can be constructed through the usual method of
inverting the $t$-test. This procedure gives the widely-used interval estimator
\begin{equation*}
  \hat{\tau}(h) \pm q_{1-\alpha/2} V(h)^{1/2}
\end{equation*}
where $q_{1 - \alpha/2}$ is the $1 - \alpha/2$ quantile of the standard normal
distribution.

@@

CCT solve this problem by deriving the analytical form of the first-order bias
and explicitly recentering $\hat\tau(h)$. Under weaker assumptions on the
asymptotic behavior of the bandwidth, which we will specify in
Assumption~\ref{A2}, CCT show that the approximate bias of $\hat\tau(h)$ has the
form
\begin{equation*}
  \E(\hat{\tau}(h) \mid X_1,\dots,X_n) - \tau =
  h^{2}\Big[ \tfrac{\mu_{+}^{(2)}}{2}\Bf_{+}(h)
  - \tfrac{\mu_{-}^{(2)}}{2}\Bf_{-}(h) \Big]
  (1+o_{p}(1))
\end{equation*}
where $\Bf_{+}(h)$ and $\Bf_{-}(h)$ are observed quantities that depend on the
kernel, bandwidth, and running variables $X_1,\dots,X_n$; formal definitions of
these terms are given in the Mathematical Appendix as Equations~\eqref{eq:5}
and~\eqref{eq:6}. The plug-in bias-corrected estimator then requires estimates
for the second derivatives of the conditional mean from above and below the
cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$, and CCT show that these derivatives
can be estimated by fitting a second order local polynomial, i.e. one order
higher than the polynomial used to obtain $\hat{\tau}$, using a (potentially)
different pilot bandwidth $b$. Their procedure gives the bias-corrected
estimator
\begin{gather*}
  \hat{\tau}'(h, b) = \hat{\tau}(h) - h^{2}
  \Big[\tfrac{\hat{\mu}_{+}^{(2)}(b)}{2} \Bf_{+}(h)
  - \tfrac{\hat{\mu}_{-}^{(2)}(b)}{2}\Bf_{-}(h) \Big]
\end{gather*}
The variance introduced by the bias-correction term does not vanish, so the
naive confidence interval needs not only to be re-centered to correct the bias,
but also rescaled to allow for the additional variability introduced by the bias
correction, resulting in the following asymptotic approximation:
\begin{equation*}
  \frac{\hat{\tau}'(h, b) - \tau}{V'(h, b)^{1/2}} \to^d N(0,1)
\end{equation*}
with $V'(h, b) = V(h) + C(h, b)$ and $C(h, b)$ an additional variance component
generated by the bias-correction term. This new approximation can be used
instead of~\eqref{eq:1} to construct ``bandwidth robust'' confidence intervals,
and CCT provide simulation evidence that their intervals perform well in finite
samples even when the naive interval performs badly.

@@

@@

\appendix
\section{Mathematical appendix}

Define the following additional notation:
$r_p(x) = (1,\ x,\dots,\ x^p)'$,
\begin{equation*}
  (\hat{\mu}_{+}(h),\ \hat{\mu}_{+}^{(1)}(h),\ \hat\mu_{+}^{(2)}(h))' =
  \argmin_{\mu_0, \mu_1, \mu_2} \ssum[+]{i}{h} (Y_i - \mu_0 - \mu_1 X_i/h - \mu_2 (X_i/h)^2),
\end{equation*}
\begin{equation*}
(\hat{\mu}_{-}(h),\ \hat{\mu}_{-}^{(1)}(h),\ \hat\mu_{-}^{(2)}(h))' =
  \argmin_{\mu_0, \mu_1, \mu_2} \ssum[-]{i}{h} (Y_i - \mu_0 - \mu_1 X_i/h - \mu_2 (X_i/h)^2) \\
\end{equation*}
\begin{align}
  \label{eq:5}
  \Bf_+(h)
  & = (1\ \  0)\ \Big(\ssum[+]{i}{h} r_1(X_i/h) r_1(X_i/h)' \Big)^{-1}
    \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
  \label{eq:6}
  \Bf_-(h)
  & = (1\ \ 0)\ \Big(\ssum[-]{i}{h} r_1(X_i/h) r_1(X_i/h)' \Big)^{-1}
    \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
\end{align}

@@

Given~\eqref{eq:8}, it suffices to prove that
\begin{gather}
  \label{eq:9}
  \rho(V^{-1/2}(h,b) \Omega_+(h,b)'\epb_{+}^{*},\
    V^{-1/2}(h,b)\Omega_+(h,b)'\epb_{+}) \to^p 0
  \intertext{and}
  \label{eq:10}
  \rho(V^{-1/2}(h,b)\Omega_-(b)'\epb_{-}^{*},\
    V^{-1/2}(h,b)\Omega_-(b)'\epb_{-}) \to^p 0
\end{gather}
with $\epb_+$ an i.i.d. random vector of length $M_+(b)$, the $i$th element of
which is distributed as
\[
  \varepsilon_{i,+} =^d
  \begin{cases}
    Y_{m_+(1,b)} - \E(Y_{m_+(1,b)} \mid X_{m_+(1,b)})
    & \text{with probability\ } 1/M_+(b) \\
    \vdots \\
    Y_{m_+(M_+(b),b)} - \E(Y_{m_+(M_+(b),b)} \mid X_{m_+(1,b)})
    & \text{with probability\ } 1/M_+(b),
  \end{cases}
\]
$\epb_-$ the corresponding quantity after replacing ``+'' with ``--,'' and
$\rho$ the Mallows metric \citep{bickel1981}.\footnote{%
  For two random vectors $u$ and $v$ with finite 2nd moments, $\rho(u, v)$
  is defined as
  \begin{equation*}
    \rho(u, v) = \inf\nolimits_{(U, V)\ s.t.\ U =^d u,\ V =^d v}
    \big(\E \lVert U - V \rVert^2\big)^{1/2}.
  \end{equation*}}

We will only prove~\eqref{eq:9} since the proof of~\eqref{eq:10} is
identical. By Theorem 2.1 of \cite{freedman1981}, we have
\begin{align*}
  \rho(V^{-1/2}(h,b) \Omega_+(h,b)'\epb_{+}^{*},\
  &V^{-1/2}(h,b) \Omega_+(h,b)'\epb_{+}) \\
  &\leq \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times
    \tr(V^{-1/2}(h,b) \Omega_+(h,b)' \Omega_+(h,b)V^{-1/2}(h,b)) \\
  &= \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times O_{p^{*}}(1),
\end{align*}
the second line holding as a consequence of CCT's Lemma SA1. So it suffices
to show that $\rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \to^{p^{*}} 0$. Let
$\dot{\varepsilon}_i$ be an i.i.d. sequence randomly drawn from $\epb_+$
with replacement and let
$\bar{\varepsilon} = (1/M_+(b)) \osum[+]{i}{b} \dot{\varepsilon}_i$. Then,
using the same arguments as \cite{freedman1981}, we have the upper bound
\begin{equation*}
  \rho(\varepsilon_{+,1}^*, \varepsilon_{+,1})
  \leq
  \bar\varepsilon^2 +
  (2/M_+(b)) \osum[+]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2
  + \rho(\dot\varepsilon_1, \varepsilon_{+,1}).
\end{equation*}
But $\bar\varepsilon^2 \to^p 0$ by the LLN,
\[
  (1/M_+(b)) \osum[+]{i}{b}
  \E((\hat\varepsilon_i - \varepsilon_i)^2 \mid X_i) \to 0
\]
by CCT's Lemma SA1, and
$\rho(\dot\varepsilon_1, \varepsilon_{+,1}) \to^p 0$ by Lemma~8.4 of
\cite{bickel1981}.\qed

>>>>

\section{Introduction}
Regression Discontinuity (RD) designs have emerged in the last decade as an
important and popular research design strategy for analyzing the causal impact
of policies and interventions in several fields of the social sciences,
including economics, political science, public policy, and sociology.
This research strategy exploits the fact that many programs use somewhat
arbitrary thresholds to determine whether or not to provide a ``treatment,''
usually relying on some type of score, which this literature calls a ``running
variable.'' In its basic version, the sharp RD,  individuals or groups with score above a
certain threshold receive treatment while the ones below that cutoff are left
untreated.
The identification of the treatment effect at the threshold is then based on
comparing treated and untreated units at the cutoff. When a subject's
position just above or below the cutoff is credibly not related to
other factors impacting outcomes, including their unobserved
characteristics, differences between treated and untreated individuals
at the cutoff can be plausibly attributed to the treatment alone. As a
practical matter this involves comparing units within a bandwidth just
above and just below the threshold.

@@

Since the conditions for identification only need to hold in a neighborhood
around the cutoff, $\mu_+$ and $\mu_-$ can be estimated by extrapolating from a
local polynomial regression.  We will focus here on local linear
regression.\footnote{%
  See \cite{HTV2001}, \cite{Porter03} or \cite{FanGijbels92} for discussions of
  the properties of local polynomial regressions for boundary problems. The
  bootstrap algorithm proposed in this paper can be extended to accommodate
  higher order polynomials discontinuities in the derivatives of the conditional
  expectation, like ``Kink RD'' design \citep{card2009b}.} %
For this model, if $h$ represents a bandwidth parameter, the estimator of
$\tau$, $\hat\tau(h)$, is defined as
\begin{equation*}
  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
\end{equation*}
with
\begin{align*}
  (\hat {\mu}_{+}(h),\ \hat {\mu}^{(1)}_{+}(h))'
  &= \argmin_{\mu, \beta} \sum_{i=1}^{n}
  \1\{h > X_{i} \geq 0\} (Y_{i} - \mu - X_{i} \beta)^{2}
\intertext{and}
  (\hat {\mu}_{-}(h),\hat {\mu}^{(1)}_{-}(h))'
  &= \argmin_{\mu,\beta} \sum_{i=1}^{n}
  \1\{0 > X_{i} > -h \} (Y_{i} - \mu - X_{i} \beta)^{2}.
\end{align*}
Conventional (naive) confidence intervals can be calculated by using an
asymptotic approximation for $\hat\tau(h)$. In particular, if
\begin{gather}
  \label{eq:1}
  \frac{\hat{\tau}(h)-\tau}{\sqrt{V(h)}} \to^d N(0,1),
  \intertext{with}
  \notag
  V(h) \big/ \V(\hat\tau(h) \mid X_{1},\dots,X_{n}) \to^p 1
\end{gather}
then valid confidence intervals can be constructed through the usual method of
inverting the $t$-test.\footnote{%
  The mathematical appendix of this paper gives a precise definition for
  $V(h)$.} %
This procedure gives the widely-used interval estimator
\begin{equation*}
  \hat{\tau}(h) \pm q_{1-\alpha/2} V(h)^{1/2}
\end{equation*}
where $q_{1 - \alpha/2}$ is the $1 - \alpha/2$ quantile of the standard normal
distribution.

@@

CCT solve this problem by deriving the analytical form of the first-order bias
and explicitly recentering $\hat\tau(h)$. Under weaker assumptions on the
asymptotic behavior of the bandwidth, which we will specify in
Assumption~\ref{A2}, CCT show that the approximate bias of $\hat\tau(h)$ has the
form
\begin{equation*}
  \E(\hat{\tau}(h) \mid X_1,\dots,X_n) - \tau =
  h^{2}\Big[ \tfrac{\mu_{+}^{(2)}}{2}\Bf_{+}(h)
  - \tfrac{\mu_{-}^{(2)}}{2}\Bf_{-}(h) \Big]
  (1+o_{p}(1))
\end{equation*}
where $\Bf_{+}(h)$ and $\Bf_{-}(h)$ are observed quantities that depend on the
kernel, bandwidth, and running variables $X_1,\dots,X_n$; formal definitions of
these terms are given in the Mathematical Appendix as Equations~\eqref{eq:5}
and~\eqref{eq:6}. The plug-in bias-corrected estimator then requires estimates
for the second derivatives of the conditional mean from above and below the
cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$, and CCT show that these derivatives
can be estimated by fitting a second order local polynomial, i.e. one order
higher than the polynomial used to obtain $\hat{\tau}$, using a (potentially)
different pilot bandwidth $b$. Their procedure gives the bias-corrected
estimator
\begin{gather*}
  \hat{\tau}'(h, b) = \hat{\tau}(h) - h^{2}
  \Big[\tfrac{\hat{\mu}_{+}^{(2)}(b)}{2} \Bf_{+}(h)
  - \tfrac{\hat{\mu}_{-}^{(2)}(b)}{2}\Bf_{-}(h) \Big]
\end{gather*}
The variance introduced by the bias-correction term does not vanish, so the
naive confidence interval needs not only to be re-centered to correct the bias,
but also rescaled to allow for the additional variability introduced by the bias
correction, resulting in the following asymptotic approximation:
\begin{equation*}
  \frac{\hat{\tau}'(h, b) - \tau}{V'(h, b)^{1/2}} \to^d N(0,1)
\end{equation*}
with $V'(h, b) = V(h) + C(h, b)$ and $C(h, b)$ an additional variance component
generated by the bias-correction term.\footnote{%
  $C(h,b)$ and $V(h)$ are defined precisely in the mathematical appendix.} %
This new approximation can be used
instead of~\eqref{eq:1} to construct ``bandwidth robust'' confidence intervals,
and CCT provide simulation evidence that their intervals perform well in finite
samples even when the naive interval performs badly.

@@

\section{Application}\label{application}

In this section, we apply the bootstrap procedure to the data used in \cite{ludwig2007}.\footnote{The data is publicly available from http://faculty.econ.ucdavis.edu/faculty/dlmiller/statafiles/.} In their paper, the effects of Head Start application assistance on health and schooling were investigated under standard RD design.

In 1965, the Head Start program was established to help poor children age three to five and their families. The program elements include parent involvement, nutrition, social services, mental health services and health services. To promote this program in the most needing area, the Office of Economic Opportunity provided grant-writing assistance to the poorest 300 counties in the United States based on the 1960 poverty rate. So the poverty rate of the 300th poorest county serves as a sharp cutoff of treatment. It is shown in \cite{ludwig2007} that the 228 ``treatment" counties with poverty rates 10 percentage points above this cutoff have average Head Start spending per four-year-old as twice as that for 349 ``control" counties with poverty rates 10 percentage points below this cutoff.

\cite{ludwig2007} utilized this fact and estimated the ``intent-to-treat" effect: the effect of proposal developing assistance on health and schooling. The mortality data come from Vital statistics, which provide information on cause of death and age at death. They limited the causes of death to those which could be affected by Head Start health services and found a large drop in mortality rates of children five to nine years of age over the period of 1973-1983. They also found some evidence for a positive effect on schooling from decennial census data.

We reestimate the ATE on health and schooling with robust procedures. To be specific, we apply both robust procedure proposed by CCT and bootstrap procedure introduced in this paper. For completeness, we also reproduce the original results in \cite{ludwig2007}.\footnote{However, we were unable to reproduce their point estimates for the ATE under the nonparametric setting using triangular kernel, which was documented in their paper. Instead, we used uniform kernel and obtained exactly the same results as theirs.} However, there are two issues which make direct comparison difficult. First, \cite{ludwig2007} reported percentile-T bootstrapped p-value while both robust procedures do not. Second, both robust procedures provide confidence interval, which is not available in \cite{ludwig2007}. To complete this comparison, we calculate the conventional confidence interval for estimates in \cite{ludwig2007} and include their percentile-T bootstrapped p-value as well.\footnote{Since these are two different ways for statistical interence, they may disagree with each other.} We use the AMSE-optimal bandwidth proposed by CCT and uniform kernel. In the bootstrap procedure, we use 500 bootstraps for bias correction and 999 for confidence interval.

Table \ref{tbl:2} gives the results on the Head Start targeted mortality of children five to nine years of age over the period of 1973-1983. Instead of choosing an optimal bandwidth, \cite{ludwig2007} adopted three candidate bandwidths 9, 18, and 36. Their estimates indicate that Head Start assistance lowers the targeted mortality rate by -1.895, -1.198 and -1.114 respectively, which are not very sensitive to the choice of bandwidths in this range. These ATEs are also significant different from zero (with p-value 0.036, 0.081 and 0.027) based on percentile-T bootstrapped p-value. The statistic inference changes when conventional analytical confidence interval is used, which includes zero for bandwidth 9 and 18. Results from the two robust procedures are similar to each other but greatly differ from the original estimates. The estimated ATEs are as high as -3.795 from CCT and -3.792 from bootstrap. Both are significantly different from zero, though the confidence intervals are also  very wide. This is mostly due to much smaller bandwidths ($h=3.888, b=6.807$), which are believed to reduce the bias at the cost of larger variance.

\begin{table}[ht]
	\centering
	\begin{tabular}{lccccc}
		\toprule
		          & ATE    & 95\% CI          &P-value& h     & b     \\ 
		\midrule
		LM(2007)  & -1.895 & (-3.930, 0.139)  & 0.036 & 9     &       \\ 
		LM(2007)  & -1.198 & (-2.561, 0.165)  & 0.081 & 18    &       \\ 
		LM(2007)  & -1.114 & (-2.138, -0.090) & 0.027 & 36    &       \\ 
		CCT       & -3.795 & (-7.037, -0.554) &       & 3.888 & 6.807 \\ 
		Bootstrap & -3.792 & (-6.512, -0.262) &       & 3.888 & 6.807 \\ 
		\bottomrule
	\end{tabular}
	\caption{The effect of Head Start assistance on mortality. The first three rows come from Table 3 in \cite{ludwig2007} except ``95\% CI", which is calculated using conventional approach. The last two rows list results from two robust procedures.}
	\label{tbl:2}
\end{table}

Table \ref{tb:3} gives the results on schooling for the cohort aged 18-24 in 1990. The measurement of schooling is the fraction of people with high school or more in Panel A and the fraction of people with some college or more in Panel B. A bandwidth of 7 is used in \cite{ludwig2007}. Their estimates suggest that Head Start assistance increases the fraction of people with high school or more by 3\% and the fraction of people with some college or more by 3.7\%. Both are significantly different from zero based on percentile-T bootstrapped p-value and conventional analytical confidence interval. The two robust procedures are again very similar to each other and give slightly larger point estimates in both panels. In Panel A, the ATE increases from 0.030 to 0.055(CCT) and 0.054(bootstrap). In Panel B, the ATE increases from 0.037 to 0.051(CCT) and 0.052(bootstrap). In contrast to the striking differences between estimates in \cite{ludwig2007} and estimates from robust procedures for mortality, the differences in Table \ref{tb:3} are much smaller.

\begin{table}[ht]
	\centering
	\begin{tabular}{lccccc}
		\toprule
		& ATE   & 95\% CI        &P-value& h     & b                \\ 
		\midrule
		&\multicolumn{5}{c}{Panel A: Fraction high school or more}  \\

		LM(2007)  & 0.030 & (0.003, 0.057) & 0.032 & 7     &                  \\ 
		CCT       & 0.055 & (0.014, 0.096) &       & 3.671 & 8.618            \\ 
		Bootstrap & 0.054 & (0.013, 0.096) &       & 3.671 & 8.618            \\

		&&&&& \\
		&\multicolumn{5}{c}{Panel B: Fraction some college or more} \\		
		LM(2007)  & 0.037 & (0.002, 0.073) & 0.031 & 7     &                  \\ 
		CCT       & 0.051 & (0.004, 0.099) &       & 5.076 & 10.251           \\ 
		Bootstrap & 0.052 & (0.001, 0.094) &       & 5.076 & 10.251           \\ 
		\bottomrule
	\end{tabular}
	\caption{The effect of Head Start assistance on education for cohort 18-24 in 1990. Panel A uses the fraction of people with high school or more as dependent variable. Panel B uses the fraction of people with some college or more as dependent variable. The first row in each panel comes from Table 4 in \cite{ludwig2007} except ``95\% CI", which is calculated using conventional approach. The last two rows in each panel list results from two robust procedures.}
	\label{tb:3}
\end{table}

To briefly summarize, the bootstrap procedure performs similarly to the robust estimator proposed by CCT in above applications. In Table \ref{tbl:2} and \ref{tb:3}, these two approaches give almost identical point estimates and interval estimates.

@@

\newpage
\appendix
\section{Mathematical appendix}
Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
everywhere else. Define the following additional notation (largely
introduced by CCT): $r_p(x) = (1,\ x,\dots,\ x^p)'$,
\begin{align*}
  (\hat{\mu}_{+}(h),\ \hat{\mu}_{+}^{(1)}(h),\ \hat\mu_{+}^{(2)}(h))'
  &= \argmin_{\mu_0, \mu_1, \mu_2} \ssum[+]{i}{h}
    (Y_i - \mu_0 - \mu_1 X_i/h - \mu_2 (X_i/h)^2) \\
  (\hat{\mu}_{-}(h),\ \hat{\mu}_{-}^{(1)}(h),\ \hat\mu_{-}^{(2)}(h))'
  &= \argmin_{\mu_0, \mu_1, \mu_2} \ssum[-]{i}{h}
    (Y_i - \mu_0 - \mu_1 X_i/h - \mu_2 (X_i/h)^2)
\end{align*}
\begin{align}
  \notag
  \Gamma_{+,p}(h) &= \tfrac{1}{nh} \ssum[+]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
  \notag
  \Gamma_{-,p}(h) &= \tfrac{1}{nh} \ssum[-]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
  \notag
  \Psi_{+,p,q}(h,b)
  &= \tfrac{1}{nhb} \ssum[+]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
    \V(Y_i \mid X_i) \\
  \notag
  \Psi_{-,p,q}(h,b)
  &= \tfrac{1}{nhb} \ssum[-]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
    \V(Y_i \mid X_i) \\
  \label{eq:5}
  \Bf_+(h)
  & = e_0' \Gamma_{+,1}^{-1}
    \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
  \label{eq:6}
  \Bf_-(h)
  & = e_0' \Gamma_{-,1}^{-1}
    \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
\end{align}

Also, for reference, define the variance terms
\begin{equation*}
  V(h)
  = e_0' \Big(\tfrac{1}{n} \Gamma_{-,1}^{-1} \Psi_{-,1} \Gamma_{-,1}^{-1}
  + \tfrac{1}{n} \Gamma_{+,1}^{-1} \Psi_{+,1} \Gamma_{+,1}^{-1}\Big) e_0
\end{equation*}
and
\begin{multline*}
  C(h,b) =
  n^{-1} e_2' \Big[
    \Gamma_{+,2}^{-1}(b) \Psi_{+,2,2}(b,b) \Gamma_{+,2}^{-1}(b) \Bf^2_+(h) +
    \Gamma_{-,2}^{-1}(b) \Psi_{-,2,2}(b,b) \Gamma_{-,2}^{-1}(b) \Bf^2_-(h)
    \Big] e_2 \\
  - 2 h^2 n^{-1} b^{-2}
    e_0' \Big[
    \Gamma^{-1}_{+,1}(h) \Psi_{+,1,2}(h,b) \Gamma_{+,2}^{-1}(b) \Bf_+(h) +
    \Gamma^{-1}_{-,1}(h) \Psi_{-,1,2}(h,b) \Gamma_{-,2}^{-1}(b) \Bf_-(h)
    \Big] e_2.
\end{multline*}
See CCT for the derivation and justification of these formulas.

@@

Given~\eqref{eq:8}, it suffices to prove that
\begin{gather}
  \label{eq:9}
  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
    V'(h,b)^{-1/2}\Omega_+(h,b)'\epb_{+}) \to^p 0
  \intertext{and}
  \label{eq:10}
  \rho(V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}^{*},\
    V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}) \to^p 0
\end{gather}
with $\epb_+$ an i.i.d. random vector of length $M_+(b)$, the $i$th element of
which is distributed as
\[
  \varepsilon_{i,+} =^d
  \begin{cases}
    Y_{m_+(1,b)} - \E(Y_{m_+(1,b)} \mid X_{m_+(1,b)})
    & \text{with probability\ } 1/M_+(b) \\
    \vdots \\
    Y_{m_+(M_+(b),b)} - \E(Y_{m_+(M_+(b),b)} \mid X_{m_+(1,b)})
    & \text{with probability\ } 1/M_+(b),
  \end{cases}
\]
$\epb_-$ the corresponding quantity after replacing ``+'' with ``--,'' and
$\rho$ the Mallows metric \citep{bickel1981}.\footnote{%
  For two random vectors $u$ and $v$ with finite 2nd moments, $\rho(u, v)$
  is defined as
  \begin{equation*}
    \rho(u, v) = \inf\nolimits_{(U, V)\ s.t.\ U =^d u,\ V =^d v}
    \big(\E \lVert U - V \rVert^2\big)^{1/2}.
  \end{equation*}}

We will only prove~\eqref{eq:9} since the proof of~\eqref{eq:10} is
identical. By Theorem 2.1 of \cite{freedman1981}, we have
\begin{align*}
  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
  &V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}) \\
  &\leq \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times
    \tr(V'(h,b)^{-1/2} \Omega_+(h,b)' \Omega_+(h,b)V'(h,b)^{-1/2}) \\
  &= \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times O_{p^{*}}(1),
\end{align*}
the second line holding as a consequence of CCT's Lemma SA1. So it suffices
to show that $\rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \to^{p^{*}} 0$. Let
$\dot{\varepsilon}_i$ be an i.i.d. sequence randomly drawn from $\epb_+$
with replacement and let
$\bar{\varepsilon} = (1/M_+(b)) \osum[+]{i}{b} \dot{\varepsilon}_i$. Then,
using the same arguments as \cite{freedman1981}, we have the upper bound
\begin{equation*}
  \rho(\varepsilon_{+,1}^*, \varepsilon_{+,1})
  \leq
  \bar\varepsilon^2 +
  (2/M_+(b)) \osum[+]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2
  + \rho(\dot\varepsilon_1, \varepsilon_{+,1}).
\end{equation*}
But $\bar\varepsilon^2 \to^p 0$ by the LLN,
\[
  (1/M_+(b)) \osum[+]{i}{b}
  \E((\hat\varepsilon_i - \varepsilon_i)^2 \mid X_i) \to 0
\]
by CCT's Lemma SA1, and
$\rho(\dot\varepsilon_1, \varepsilon_{+,1}) \to^p 0$ by Lemma~8.4 of
\cite{bickel1981}.\qed
